\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-06 doc/paper.tex
extend conclusions

We presented \fs, a Mathematica package, which generates fast and
modular spectrum generators for non-minimal SUSY models.  [TODO:
That's basically all, but we could add more.]

>>>>

We presented \fs, a Mathematica package, which generates fast and
modular spectrum generators for non-minimal SUSY models.  It comes
with plenty of predefined models for the CMSSM, NMSSM, USSM, \ESSM,
MRSSM etc., which can be used out of the box.  In particular the CMSSM
and NMSSM spectrum generators constitute alternatives for to the
existing ones Softsusy, SPheno and NMSPEC.  We have shown that the
generated source code can be influenced at two different levels: The
\mathematica level where the user provides a model file, and the C++
level where the generated objects can be easily exchanged, extended,
modified and reused.  This provides great flexibility for creating
custom spectrum generators for both the most common and most
extraordinary models.
